\normalfont \normalsize \textsc{Exoplanet Patchy Cloud Project} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Note for last two weeks\\ \horrule{2pt} \\[0.5cm]

### 2014-11-21 summary/dataReduction1.tex
start to write psf fitting journal

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Data Preparation\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Cross correlation has the best performance for locating the
  centroids of star images.
\item Bicubic interpolation generates smaller RMS fluctuation
  comparing to \texttt{FSHIFT.pro} when shift images, but does not
  strictly obey flux conservation. \texttt{FSHIFT.pro} strictly keeps
  the conservation of flux. Bicubic interpolation causes artifacts
  around the star images.
\end{enumerate}

\section{Centroid of Primary Star}
4 methods to locate the centroid of the primary objects were tested
for all 78 cosmic ray removed images of ABPIC-B. I compared the 4 sets
of results in order to determine the best method to find star image
centroid in this situation where the image is slightly saturated.\par

\subsection{Method Introduction}

\begin{enumerate}
\item \texttt{CNTRD.PRO}\\
  IDL routine \texttt{CNTRO.PRO} locates the position where the X
  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
  can be adjusted with parameter \texttt{EXTENDBOX}.\par
\item \texttt{GCNTRD.PRO}\\
  IDL routine \texttt{GCNTRD.PRO} fits the star image with a 2D-Gaussian
  function to search for centroid. The search area cannot be defined
  in this routine. \texttt{GCNTRD.pro} is likely to fail when the
  initial guess of centroid coordinates are far away from the true
  values. This is inconvenient for pipeline scenario, where images
  of different dithering positions are assigned with same initial
  values for fitting. In practice, I ran \texttt{CNTRD.PRO} before
  \texttt{GCNTRD.PRO} to provide initial values for Gaussian fitting.\par
\item Cross Correlation\\
  Calculate the cross correlation value to align images. The images
  taken with different rolling angle were treat separately. Images
  taken in 1st, 3th, and 5th orbits were calculated cross correlation
  with the first image in 1st orbit and images taken in 2nd, 4th, and
  6th orbits with first image in 2nd orbit.\par
 \item World Coordinate System(WCS)\\
   Use WCS to align every image. The treatment with different rolling
   angles is the same as cross correlation method. Centroids were
   calculated with IDL routine \texttt{XYXY.pro}.\par
\end{enumerate}

\subsection{Result Comparison}
Figure \ref{fig:x_off} and \ref{fig:y_off} demonstrates the
distributions of centroid offsets of \texttt{GCNTRD.pro}, cross
correlation, and WCS relative to the \texttt{CNTRD.pro} method in $x$
and $y$ direction. \par

According to the two plots, most of results calculated with all four
methods are constrained within $\pm 0.2$ pixels. Both in $x$ and $y$
directions, the histograms of \texttt{GCNTRD.pro} offsets have a
fairly strange shape, while the distributions of cross correlation and
WCS methods' offsets show a Gaussian like shape. In $x$-direction, the
distributions of cross correlation and WCS have similar behavior that
the centers of two histograms both have $\sim -0.1$ pixels offset. In
$y$ direction, histogram of cross correlation demonstrates that the
results for cross correlation and \texttt{CNTRD.pro} are well
agreed. The histogram of WCS is skewed and has a $\sim -0.1$ pixels
offset.\par

To sum, \texttt{GCNTRD.pro} method has the worst performance. In
$x$-direction, the results for cross correlation and WCS agrees well
and in $y$-direction the results for cross correlation and
\texttt{CNTRD.pro} agrees well. Thus cross correlation method performs
best.\par

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{x_off}
  \caption{$x$-direction offset histogram}
  \label{fig:x_off}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{y_off}
  \caption{$y$-direction offset histogram}
  \label{fig:y_off}
\end{figure}

\section{Image shift and interpolation algorithm}

I tested two image shift methods that uses two different interpolation
algorithms. The two algorithms are bicubic interpolation and bilinear
interpolation(used by  IDL routine \texttt{FSHIFT.pro}).\par

To evalueate the two shift methods, the image is shifted in a random direction
with a specific length and then shifted back. Both the root mean
square and mean flux change between the original image and the
modified image  will be calculated as following:
\begin{align}
  &\Delta_{\mathrm{rms}} = \frac{\sqrt{(\mathrm{img}_{0} -
      \mathrm{img_{shifted}})^{2}}}{N_{\mathrm{pixels}}}\\
  &\bar{\Delta} = \frac{\mathrm{img}_{0} - \mathrm{img_{shifted}}}{N_{\mathrm{pixels}}}
\end{align}

The results are demonstrated with figure \ref{fig:shifted}.
\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{test_shift}
  \caption{Root mean square and mean flux change betwenn the original image and the modified image as a function of shift length.}
  \label{fig:shifted}
\end{figure}
\begin{enumerate}
\item bicubic interpolation comes up with a smaller RMS change, thus
  the error generated by image shift will be smaller with a bicubic interpolation.
\item \texttt{FSHIFT.pro} strictly keeps flux conserved, while bicubic
  interpolation ends up with a $\sim \pm 0.003$ per pixel change in flux.
\item bicubic interpolation will generate ringing artifacts(figure \ref{fig:ringing})
\end{enumerate}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\textwidth]{interpolated}
  \caption{Ringing artifacts generated by bicubic interpolation.}
  \label{fig:ringing}
\end{figure}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%   ----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

@@

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Note for last two weeks\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\maketitle % Print the title
\section{Ramp effect}
\begin{quote}
  \begin{itemize}
\item 2 ways
\item check the paper
 \end{itemize}
\end{quote}

\begin{itemize}
\item  In \textsl{Wilkins et. al. 2013}\\

    The ramp effect is neglectable when exposure level is below \textbf{30000} electrons per pixel.

\item In \textsl{Deming et. al. 2013}\\

    They expected ramp effect to be weakly detectable in their data
    when their exposure level is about \textbf{40000} electrons per pixel.
\end{itemize}

 In our data, the maximum exposure level at the secondary image is $\sim$2000 e$^-$ per pixel, which is far below 30000 e$^-$ per pixel. Therefore the ramp effect in our case should be small enough.

\section{ PSF photometry}
>plot PSF photometry with aperture photometry

\subsection{ generate PSF}
1. for the same filter and the same rolling angle, the center of the secondary is not exactly at the same position. Using mpfit2dpeak to measure the secondary centroid, the maximum difference in both x and y direction could be as large as 0.05 pixel (measured by cross correlation). *This effect would enlarge the  fwhm of the synthesis PSF.*

-> align the image again when generating PSF
- fshift (a linear interpolation) will slightly change the PSF -- enlarge the FWHM, this problem will be alleviate by oversampling with a cubic interpolation, but could not be eliminated
- without second alignment with secondary object, synthetic PSF FWHM -- 1.93 pixels
- align again with secondary object, synthetic PSF FWHM -- 2.00 pixels.

2. *how to normalize the PSF?  
now, I use the flux in 5 pixel to normalize

3. Large chisq  
- caused by underestimated of error?

>aperture radius vs standard deviation
>use aper.pro  to measure photometry and uncertainty

Optimum aperture size is related to the estimation of background fluctuation. A difference of 1 count/pixel difference in background fluctuation could lead to 0.5 pixel change in optimum aperture radius. Aper.pro routine provides 2 ways to define sky fluctuation:
1. ﻿﻿﻿﻿directly input sky level and fluctuation when calling the program. The sky value and sigma should be calculated before hand.
2. input annulus radii of the sky region and let the program calculate it. The sky region here must be an annulus around the secondary object in this case.

I choose to calculate the sky fluctuation separately rather than let aper.pro calculate.

1. if the annulus is too close to the secondary object, the flux of the secondary image could contaminate the sky and end up with a higher estimation of sky level and an inaccurate estimate of sky fluctuation.    
2. The annulus radii cannot be large too. Because the slight change of PSF, the image of the primary cannot be removed completely. The residual of the primary image fluctuate largest at the center region as well as the diffraction spikes region.  When the annulus radii get slightly larger, the annulus would include these region. If the annulus radii get even larger to avoid these region, it would cause an under-estimate of the sky fluctuation because the area of this annulus is not affected by psf subtraction.

The optimum aperture radius turned out to be very small, it ranges from 2.8 to 3.5 pixels. which is only 1 pixel larger than fwhm of the image, which is 1.8 pixels.

\section{Analyze light curve}
>1. is the source varying
>2. what is the amplitude in two colors

According to aperture photometry, the peak to peak variation is about 2%
>3. is the change periodic
At least, it is difficult to find a period by eye.

>4. are the changes in the filter correlated

5. color magnitude diagram (Apai 2013) 
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
